Disparity through time - simplified and for appendix

### 2017-12-08 analyses/04-figure-dtt.Rmd
Add appendix figures

@@

pdf("../manuscript/figures/fig-dtt.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

>>>>

```{r}
out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))

```{r}
out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))

```{r}
out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))

```{r}
out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))

pdf("../manuscript/figures/fig-dtt-age.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

Repeat for epochs
-----------------
```{r}
slug <- "Beck2014"
```

@@

pdf("../manuscript/figures/fig-dtt-epoch.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```
